\setlength{\parindent}{0cm}
\setlength{\parskip}{0.5em}

\begin{samepage}
  \hrule
  \section*{experience}
\end{samepage}

\noindent\begin{minipage}[t]{0.5\textwidth}
  \subsection*{Incremental IT}
\end{minipage}
\noindent\begin{minipage}[t]{0.5\textwidth}
  \flushright
  July 2018 - Current
\end{minipage}

\emph{Software engineer contractor}

\begin{itemize}
\item I provide technical solutions to on-demand business problems.
  Specializing in web technologies and Node.js, PostgreSQL, and Heroku (my
  preferred hosting platform), I develop products for my clients' businesses.
\item I work on corporate websites, dynamic web applications, and data APIs.
  My products are responsive on all the popular web browsers and they serve
  users on desktops, laptops, mobile devices, and tablets.
\end{itemize}

\noindent\begin{minipage}[t]{0.5\textwidth}
  \subsection*{SpotX}
\end{minipage}
\noindent\begin{minipage}[t]{0.5\textwidth}
  \flushright
  September 2016 - July 2018
\end{minipage}

\emph{Software engineer}

\begin{itemize}
\item Member of a team creating native mobile client software development kits
  (SDKs) to allow publishers to serve video advertisements within their
  applications.

\item Helped create the next iteration of SpotX's SDK offering that serves
  millions of advertisement impressions daily.

\item Improved product quality and developer feedback by introducing a number of
  tools and practices. These include \emph{the reproducible build},
  \emph{continuous integration} (with Jenkins), and \emph{specification by
    example}.

\item Increased developer confidence in making changes and deploying code to
  production by building out a comprehensive test suite as part of the build
  pipeline.
\end{itemize}

\begin{minipage}[t]{0.6\textwidth}
  \subsection*{Cambium Consulting - Incremental IT}
\end{minipage}
\noindent\begin{minipage}[t]{0.4\textwidth}
  \flushright
  September 2017 - March 2018
\end{minipage}

\emph{Software engineer contractor}

\begin{itemize}
\item Worked with a team creating a greenfield underwriting platform to
  analyse bank statements and extract data to assist in identifying a business'
  loan risk potential.

\item Improved the feedback loop by introducing a CircleCI pipeline, in addition
  to fleshing out the testing infrastucture across the Clojure/ClojureScript
  stack.

\item Increased release safety and confidence by creating a staging environment
  in Heroku for the purpose of exploratory testing a production-like environment
  before release.
\end{itemize}

\noindent\begin{minipage}[t]{0.55\textwidth}
\subsection*{Trilogy Education - Denver University}
\end{minipage}
\noindent\begin{minipage}[t]{0.45\textwidth}
  \flushright
  March 2017 - October 2017
\end{minipage}

\emph{Assistant instructor}

\begin{itemize}
\item Partnered with Denver University to assist in teaching a part-time
  course on full-stack web development.

\item Taught and mentored over 60 students in fundamental programming practice
  and the use of emerging tools in the frontend and backend (Node.js)
  ecosystems.
\end{itemize}

\noindent\begin{minipage}[t]{0.5\textwidth}
  \subsection*{Good Travel Software}
\end{minipage}
\noindent\begin{minipage}[t]{0.5\textwidth}
  \flushright
  Summer 2015
\end{minipage}

\emph{Software developer intern}

\begin{itemize}
\item Led to completion the construction of the front-end of a predictive
  analytics platform. This improved the firm's product offering with a web
  application that offers intuitive visualisations and mappings of hundreds of
  thousands of data points in multiple languages.

\item The application provides an interface for clients to more accurately and
  intuitively track user demand and car supply, enabling them to more
  effectively manage their fleet of vehicles.
\end{itemize}

\noindent\begin{minipage}[t]{0.5\textwidth}
  \subsection*{MIAC Acadametrics Ltd}
\end{minipage}
\noindent\begin{minipage}[t]{0.5\textwidth}
  \flushright
  Summer 2014
\end{minipage}

\emph{Software developer intern}

\begin{itemize}
\item Empowered MIAC and its clients to exchange files more quickly and
  securely than the existing FTP approach by building a greenfield, web-based,
  file-exchange application.
\end{itemize}

\noindent\begin{minipage}[t]{0.5\textwidth}
  \subsection*{Hard Medium Soft Ltd}
\end{minipage}
\noindent\begin{minipage}[t]{0.5\textwidth}
  \flushright
  Summer 2013
\end{minipage}

\emph{Software developer intern}

\begin{itemize}
\item Completed a contract to redevelop an accounting platform. I reduced the
  existing codebase by hundreds of lines of code, modularised many of the
  existing features, and remade the UI. This resulted in a codebase that was
  easier to work with and a finished product with an improved user experience.
\end{itemize}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../../master/charlie_hebert_resume"
%%% End:
