\begin{samepage}
  \hrule
  \section*{projects}
\end{samepage} {\small Note: The demos may take more than a moment to load the
  first time (free hosting). }

\noindent\begin{minipage}[t]{0.8\textwidth}
  \subsection*{HTML5 game}
\end{minipage}
\noindent\begin{minipage}[t]{0.2\textwidth}
  \flushright
  Autumn 2018
\end{minipage}

\href
{https://github.com/chooie/incremental_it/tree/master/src/application/client/ui}
{github.com/chooie/incremental\_it} ---
\href{https://www.incremental-it.com/game}{Demonstration}

\begin{itemize}
  {\small
  \item A minimal top-down shooter that works across mobile, tablet, and desktop.
  \item Learnt about responsiveness, optimization, and making a game in a
    browser environment.
  }
\end{itemize}

\noindent\begin{minipage}[t]{0.8\textwidth}
  \subsection*{Node.js HTML template engine}
\end{minipage}
\noindent\begin{minipage}[t]{0.2\textwidth}
  \flushright
  Summer 2018
\end{minipage}

\href
{https://github.com/chooie/js_to_html/tree/master/src/application/shared}
{github.com/chooie/js\_to\_html} ---
\href
{https://incremental-it.com}{Demonstration}

\begin{itemize}
  {\small
  \item Simpler and more powerful, in my opinion, to other template languages
    that force a new paradigm or special syntax on you.
  \item All the benefits of a template language, without leaving the toolset
    provided by JavaScript.
  }
\end{itemize}


\noindent\begin{minipage}[t]{0.8\textwidth}
  \subsection*{Application templates for testing}
\end{minipage}
\noindent\begin{minipage}[t]{0.2\textwidth}
  \flushright
  Summer 2018
\end{minipage}

\href
{https://github.com/chooie/test-driven-clj-cljs}
{github.com/chooie/test-driven-clj-cljs} ---
\href
{https://chooie-my-app-production.herokuapp.com/}
{Demonstration}

\href
{https://github.com/chooie/automatopia-nodejs}
{github.com/chooie/automatopia-nodejs} ---
\href
{https://automatopia-nodejs-production.herokuapp.com/}
{Demonstration}

\begin{itemize}
  {\small
  \item Learnt about testing at the unit, integration, and end-to-end level in
    the Clojure and Node.js ecosystems.
  \item Explored testing CSS, an uncommon practice.
  }
\end{itemize}

\noindent\begin{minipage}[b]{0.8\textwidth}
  \subsection*{Maze solver}
\end{minipage}
\noindent\begin{minipage}[b]{0.2\textwidth}
  \flushright
  Summer 2016
\end{minipage}

\href{https://github.com/chooie/maze-solver} {github.com/chooie/maze-solver}

\begin{itemize}
  {\small
  \item Developed my understanding of functional programming and the Clojure
    environment by creating an application to solve mazes.
  \item A user can pass in an unsolved maze - the program will then permute
    paths through the maze until it finds the optimal solution.
  }
\end{itemize}

\noindent\begin{minipage}[b]{0.8\textwidth}
  \subsection*{Clock.js}
\end{minipage}
\noindent\begin{minipage}[b]{0.2\textwidth}
  \flushright
  Spring 2015
\end{minipage}

\href{https://github.com/chooie/clock.js} {github.com/chooie/clock.js} ---
\href {https://chooie.github.io/clock.js} {Demonstration}

\begin{itemize}
  {\small
  \item Improved my understanding of drawing graphics in a web browser by
    creating a library that draws simple analog clocks and updates them in
    real-time.
  }
\end{itemize}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../../master/charlie_hebert_resume"
%%% End:
